Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-05 GNproof.tex
see purple

@@

We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The base case follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.

[induction step; see final page]

>>>>

{\color{violet} Second, we note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it is the clockwisemost propagator supported on $a_m$ in the set $\cP \setminus \cP_{m-1}$. If $p_r$ is also supported on $a_m$, if $p_r$ is outside $p_m$ in the $<_{a_m-1}$ order, then it must have been assigned before $p_m$, i.e. $r <m$. Otherwise, $p_m$ could not be the clockwise most propagator when the algorithm reached $a_m$.}

@@

We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. \st{The base case } \hlfix{The case for $l= 0$}{$l=0$ is not quite the base case} follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.

{\color{violet} Next we prove the base case of $l=1$. If $Q_1 \setminus Q_0 = \emptyset$, we are done. Else, let $q \in Q_1 \setminus Q_0$. By construction $q$ shares support with a propagators in $\Q_{0}$. Call this propagator $p_j$. By the above, $p_j \in \cP_{m-1}$. Suppose that $q \not \in \cP_{m-1}$. The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$). Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction.}

{\color{violet} Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this et is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagators in $\Q_{l-1}$. Call this propagator $p_j$. Let $v_j$ be the fourth propagator of $p_j$ in the $a_{j}-1$ ordering (not assigned to $I_i$.) We have two cases: $a_j-1 < v_j < j_m$ in any cyclice ordering, or $a_j-1 < j_m < v_j$. In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction.

In the second case, suppose $p_j$ must share an edge with $p_r \in Q_{l-2}$ and $a_j +1  = a_r$. If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering. However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen. 
} \sanote{I hadn't thought through this second case very well when I first wrote the proof. Please check.}
